\section{Universal Verification Methodology Multi-Language}\label{uvm_ml}
Verification projects consist of ready to use verification components, which are joined in a testbench. These components
are often implemented in different verification languages like SystemVerilog, \textit{e} or SystemC. For
example, when verification projects are normally implemented in \textit{e}, but some components are intellectual
property and provide UVCs implemented in SystemVerilog. This leads to the demand of re-implementing fully
operative code just to switch the verification language.\\
Such a time consuming approach to this problem can be avoided by using the \emph{Universal Verification Methodology
Multi-Language} (UVM-ML) \cite{uvm_ml_user} package. It is developed in cooperation of Advanced Micro Devices, Inc. (AMD) and Cadence Design
Systems, Inc. It is based on the \emph{Universal Verification Methodology} and extends it multi-language
functionalities. These enable the joined use of components implemented in different verification languages to build a
single testbench with minimal changes of the reused components.\\
This report focuses on the two verification languages SystemVerilog and \textit{e} both using the \emph{Universal
Verification Methodology} to show the capabilities provided by UVM-ML. The simulator used for this is the
\emph{Incisive Enterprise Simulator} developed by \emph{Cadence Design Systems, Inc.}\\
The key concepts, which provide these capabilities are described in the following section. After that it is shown how to
integrate multi-language functionalities into \emph{Incisive Enterprise Simulator} (IES). Followed by the illustration on how
to use it to create a multi-language environment, configure its sub-components and enable data communication between
components. Finally it is declared how to start a test in this environment.

\input{3_1_key_concept}
\input{3_2_integrate_ml}
\input{3_3_create_env}
\input{3_4_mapping}
\input{3_5_config}
\input{3_6_communication}
\input{3_7_seq_layering}
\input{3_8_eot}
\input{3_9_running_tb}

